Example slide presentation using slidy

### 2019-11-13 inst/rmarkdown/templates/slidy/skeleton/skeleton.Rmd

---
title: "Example slide presentation using slidy"
subtitle: "A place for a subtitle"
author: "Matthew Crump"
date: "10/31/2019"
output:
  slidy_presentation:
    self_contained: true
    theme: yeti
    incremental: true
    css: custom_css/style.css
---

@@

```{r, echo = FALSE, out.width="50%", fig.align="center"}
knitr::include_graphics("imgs/logo.png")
```

>>>>

---
title: "Example slide presentation using slidy"
subtitle: "A place for a subtitle"
author: "Matthew Crump"
date: "10/31/2019"
output:
  slidy_presentation:
    self_contained: true
    theme: yeti
    incremental: true
---

@@

```{r, echo = FALSE, out.width="50%", fig.align="center"}
plot(pressure$temperature, pressure$pressure)
```
